Communicating with convexity

### 2017-12-01 article_cvxpy.tex
just some commas and subscripts added

\subsection{Path gain}
\noindent In a physical context, the path gain from transmitter $j$ to receiver $i$, as shown in Fig.~\ref{fig:pathgain}, will depend on the distance $d_{ij}$ between them. Assuming isotropic propagation from each transmitter, given a pathloss coefficient $\alpha$ and a proportionality constant $A_i$ specific to receiver $i$, the fraction of power from $j$ that reaches $i$ is,
\begin{equation}
G_{ij} = A_i/d_{ij}^\alpha.
\end{equation}
For free space $\alpha = 2$, while in urban environments $\alpha \sim 3.5$ \cite{hata1980}. Further physical complexities, such as the stochastic effects from Rayleigh fading can be easily incorporated, whilst remaining within the DCP framework.

@@

All the parameters we will take as dimensionless to give simple numbers to work with.  The maximum available power, $P_{\text{max}}$ is set to 1.  We have chosen the background noise vector $\boldsymbol{\sigma}$ as constant for each receiver, with $\sigma_i = 5$.  Similarly, the receiver coefficient $A$ was set to $0.025$ for each receiver. \\

To generate the gain matrix $G$, we randomly sample distances from a given distribution.  For paired transmitters and receivers ($k=i$), we sample $d$ from a scaled $\beta(2,2)$ distribution, such that $d_{ii} \sim 0.2\times\text{Beta}(2,2)$.  For unpaired transmitters and receivers ($k\neq i$), we sample $d$ from a uniform distribution, such that $d_{ik} \sim \text{Uniform}(0,1)$.  This is illustrated in Figure~\ref{fig:dist}.

>>>>

\subsection{Path gain}
\noindent In a physical context, the path gain from transmitter $j$ to receiver $i$, as shown in Fig.~\ref{fig:pathgain}, will depend on the distance, $d_{ij}$, between them. Assuming isotropic propagation from each transmitter, given a pathloss coefficient, $\alpha$, and a proportionality constant, $A_i$, specific to receiver $i$, the fraction of power from $j$ that reaches $i$ is,
\begin{equation}
G_{ij} = A_i/d_{ij}^\alpha.
\end{equation}
For free space $\alpha = 2$, while in urban environments $\alpha \sim 3.5$ \cite{hata1980}. Further physical complexities, such as the stochastic effects from Rayleigh fading can be easily incorporated, whilst remaining within the DCP framework.

@@

All the parameters we will take as dimensionless to give simple numbers to work with.  The maximum available power, $P_{\text{max}}$ is set to 1.  We have chosen the background noise vector, $\boldsymbol{\sigma}$, as constant for each receiver, with $\sigma_i = 5$.  Similarly, the receiver coefficient, $A_i$, was set to $0.025$ for each receiver. \\

To generate the gain matrix, $G$, we randomly sample distances from a given distribution.  For paired transmitters and receivers ($k=i$), we sample $d$ from a scaled $\beta(2,2)$ distribution, such that $d_{ii} \sim 0.2\times\text{Beta}(2,2)$.  For unpaired transmitters and receivers ($k\neq i$), we sample $d$ from a uniform distribution, such that $d_{ik} \sim \text{Uniform}(0,1)$.  This is illustrated in Figure~\ref{fig:dist}.
